Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-14 paper.qmd
Updated Figure 10

error_plot_one_curvy_hist_selected <- ggplot(error_df_one_curvy_abs, 
      aes(x = sqrt_row_wise_total_error, 
          y = density,
          colour = factor(error_cat_n, levels = c("deselected", "selected")))) +
  geom_point(alpha=0.7) +
  scale_color_manual(values=c('#d9d9d9', '#800026')) +
  xlab(expression(e[hj])) +
  ylab("") +
  interior_annotation("b1",
                      position = c(0.95, 0.9),
                      cex = 2) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15))

error_plot_one_curvy_hist <- ggplot(error_df_one_curvy_abs,
        aes(x = sqrt_row_wise_total_error, 
            y = density,
            colour = factor(error_cat_n2, levels = c("deselected", "selected")))) +
  geom_point(alpha=0.7) +
  scale_color_manual(values=c('#d9d9d9', '#800026')) +
  xlab(expression(e[hj])) +
  ylab("") +
  interior_annotation("a1",
                      position = c(0.95, 0.9),
                      cex = 2) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15))
```

@@

design <- "
AABB
AABB
AABB
"

# Put error plot in area A, and wrap_plots in area B
error_plot_pbmc + 
  wrap_plots(nldr1c, nldr2c, nldr3c, nldr4c,
             nldr5c, nldr6c, nldr7c, nldr8c, ncol = 2) +
  plot_layout(design = design)
```

>>>>

error_df_one_curvy_abs_selected1 <- error_df_one_curvy_abs |>
  dplyr::filter(error_cat_n == "selected")

error_df_one_curvy_abs_deselected1 <- error_df_one_curvy_abs |>
  dplyr::filter(error_cat_n == "deselected")

error_plot_one_curvy_hist_selected <- ggplot(error_df_one_curvy_abs_deselected1, 
      aes(x = sqrt_row_wise_total_error, 
          y = density)) +
  geom_point(alpha=0.7, color = "#d9d9d9") +
  geom_point(data = error_df_one_curvy_abs_selected1, 
      aes(x = sqrt_row_wise_total_error, 
          y = density),
      alpha=0.7, color = "#800026", size = 3) +
  xlab(expression(e[hj])) +
  ylab("") +
  interior_annotation("b1",
                      position = c(0.95, 0.9),
                      cex = 2) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15))

error_df_one_curvy_abs_selected1 <- error_df_one_curvy_abs |>
  dplyr::filter(error_cat_n2 == "selected")

error_df_one_curvy_abs_deselected1 <- error_df_one_curvy_abs |>
  dplyr::filter(error_cat_n2 == "deselected")

error_plot_one_curvy_hist <- ggplot(error_df_one_curvy_abs_deselected1, 
      aes(x = sqrt_row_wise_total_error, 
          y = density)) +
  geom_point(alpha=0.7, color = "#d9d9d9") +
  geom_point(data = error_df_one_curvy_abs_selected1, 
      aes(x = sqrt_row_wise_total_error, 
          y = density),
      alpha=0.7, color = "#800026", size = 3) +
  xlab(expression(e[hj])) +
  ylab("") +
  interior_annotation("a1",
                      position = c(0.95, 0.9),
                      cex = 2) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15))
```

@@

design <- "
AABB
AABB
AABB
"
error_plot_pbmc + 
  wrap_plots(nldr1c, nldr2c, nldr3c, nldr4c,
             nldr5c, nldr6c, nldr7c, nldr8c, ncol = 2) +
  plot_layout(design = design)
```
